Regression Analysis and Prediction

### 2023-08-01 Writing/NatureWater/1stRoundRevision/replies/reply_to_reviewer_1.rmd

---
output:
  pdf_document:
    keep_tex: true
---
Reviewer #1 (Comments for the Author):

This manuscript assesses the impact of aquifer thickness on agricultural production during drought in the area overlying the High Plains aquifer in the central United States. The authors use crop, meteorological, and aquifer thickness data in regressions to develop relationships among these quantities. Their most important finding is the impact of aquifer thickness on productivity during drought and the ramifications for aquifer conservation efforts. I have read this manuscript over a number of times and found it of considerable interest and worthy of publication in Nature Water. However, I do have a few concerns that I wanted to bring to the attention of the authors. My most important concerns are as follows (not necessarily in order of importance):

\textcolor{blue}{Thank you for the detailed and constructive feedback on our manuscript. We have endeavored to address all your comments and suggestions, and our replies to your comments can found in blue below (original comments in black)}

@@

1. Aquifer thickness versus saturated thickness – The authors speak of ``aquifer saturated thickness'', which is a redundant term. Remember, the definition of an aquifer is a saturated unit – there is no unsaturated aquifer. Please use ``aquifer thickness'' to avoid propagating this confusing usage into the future.

\textcolor{blue}{We agree that there is some redundant use of words here. All the instances of ``saturated thickness'' and ``aquifer saturated thickness'' have been replaced by ``aquifer thickness'' in the revised manuscript.}

2. Dependence on aquifer thickness – I had a number of questions about the relationships displayed in Figure 1. First, the regression appears to have been done year by year. Are the quantiles recalculated each year to reflect that there may be changes between categories as time goes on? Second, when the authors state the lowest quantile goes from 0 to 33% are they assuming that the minimum thickness of 9 m is the zero point? Third, I assume that the county and year fixed effects are calculated as part of the regression. Are there any insights that can be gained from the interpretation of those quantities? Fourth, the authors need to point out that the same aquifer thickness can result in dramatically different transmissive characteristics. Thus, a relatively thin aquifer interval composed of coarse sands and gravels may be more resilient to drought than a much thicker aquifer dominated by fine sands and silts. Could that be a major player in the error bars in the plots? Please mention this at some point in the manuscript.

- First point: \textcolor{blue}{Quantiles are not recalculated each year. If we do so, then the same quantile would represent different aquifer thickness range every year. When modeling the impact of aquifer thickness, this is not desirable because it would be expected that different ranges of aquifer thickness would have the same impact on a farmer's ability to buffer drought risk irrespective of year.}

-  Second point: \textcolor{blue}{Thank you for highlighting this point. For the 0\% quantile, we assume a saturated thickness of 9m. This minimum of saturated thickness was selected based on \textcolor{red}{Tim, please add REFs}, which defines 9m as the minimum aquifer thickness needed to provide a functioning water supply. We have modified the text on page X lines X-X of the revised manuscript to note these points.}

-  Third point: \textcolor{blue}{Yes, country and year fixed effects are calculated as part of the regressions. However, these variables can be thought of simply as shifters that tell us how much higher average yields are in a single county relative to another county and to account for trends in yields over time. As these variables do not interact with aquifer thickness in our analysis, there would be little insights gained from analyzing these variables - and indeed it is standard to not report and analyze fixed effects terms in econometric regressions used in statistical crop-climate modeling.}

-  Fourth point: 
  \textcolor{blue}{This is an important point, which we thank the reviewer for highlighting. The reviewer is correct that unobserved factors, such as aquifer heterogeneity influencing well yield response to changes in saturated thickness, are a likely underlying cause of the uncertainty ranges found in our analyses. Variations in aquifer conductivity would alter the relationship between saturated thickness and well capacity, thereby adding noise to the relationship between saturated thickness and drought risk exposure that would contribute to uncertainty in our estimates of observed relationships between drought impacts and aquifer conditions. \textcolor{red}{(Tim, I am adding this sentence.) This noise is referred to as measurement error in the field of statistics and econometrics, and it has a well-known consequence in regression analysis, called attenuation bias. Specifically, measurement error in an explanatory variable (here, aquifer thickness) tends to bias your estimation in a way that makes the impact of the explanatory variable with measurement errors appear "less" influential than it true is. So, in our context, our estimated impact of aquifer thickness on the share of irrigation is conservative. In reality, the impact of aquifer thickness is likely to be larger.} Importantly though, our analysis shows that - even in the presence of these uncertainties - we are still able to identify statistically significant increases in drought risk exposure for irrigated agriculture as a function of declining saturated thickness. This further reinforces the importance of aquifer conditions as a determinant of adaptive capacity to drought. To highlight these points, we have added the following text in the Discussion section on page 10, the 4th paragraph of our revised manuscript:}

  \textcolor{blue}{``Similarly, unobserved variations in aquifer properties will also introduce noise into the relationships between aquifer thickness, well yields, and drought risk exposure. For example, a thinner aquifer interval composed of coarse sands and gravels may be able to supply comparable or higher well yields than a thicker aquifer dominated by fine sands and silt deposits, and hence offer greater resilience to drought despite similar or larger aquifer thickness [Butler et al., 2013, Korus and Hensen, 2020]. . These uncertainties can be considered as measurement errors in aquifer thickness as a proxy for well yield. A well-known consequence of measurement errors in regression analysis is attenuation bias [Bound and Krueger, 1991, Hyslop and Imbens, 2001]. That is, measurement error in an explanatory variable (here, aquifer thickness) tends to bias your estimation in a way that makes the impact of the explanatory variable with measurement errors appear "less" influential than it true is. Therefore, it is likely that our estimated impacts of aquifer thickness on drought risk is rather conservative, and the true impact of groundwater depletion is likely to be greater than what we reported in this article. Importantly, however, our analysis shows that - even in the presence of these uncertainties - we are still able to identify statistically significant increases in drought risk exposure for irrigated agriculture as a function of declining saturated thickness. Nonetheless, improved data on spatial variations in aquifer properties and greater monitoring of real-world changes in well capacities alongside traditional water level measurements would help to refine understanding of patterns of drought vulnerability across the HPA. This would enable more precise estimates to be made of critical tipping points in the resilience of irrigated agriculture to drought, which are needed to effectively design and target groundwater conservation policies.''}

@@

  \textcolor{blue}{New references added:}

  + \textcolor{blue}{Butler, J. J., Stotler, R. L., Whittemore, D. O., and Reboulet, E. C. (2013). Interpretation of water level changes in the High Plains aquifer in western Kansas. Groundwater, 51(2), 180-190.}

  + \textcolor{blue}{Korus, J. T., and Hensen, H. J. (2020). Depletion percentage and nonlinear transmissivity as design criteria for groundwater-level observation networks. Environmental Earth Sciences, 79(16), 382.}

  + \textcolor{blue}{John Bound and Alan B Krueger. The extent of measurement error in longitudinal earnings data: Do two wrongs make a right? Journal of labor economics, 9(1):1–24, 1991.}

  + \textcolor{blue}{Dean R Hyslop and Guido W Imbens. Bias from classical and other forms of measurement error. Journal of Business \& Economic Statistics, 19(4):475–481, 2001}

@@

  + \textcolor{blue}{Lubell, M., Blomquist, W., and Beutler, L. (2020). Sustainable groundwater management in California: A grand experiment in environmental governance. Society and Natural Resources, 33(12), 1447-1467.}

  + \textcolor{blue}{Marston, L. T., Zipper, S., Smith, S. M., Allen, J. J., Butler, J. J., Gautam, S., and David, J. Y. (2022). The importance of fit in groundwater self-governance. Environmental Research Letters, 17(11), 111001.}

## Minor points

+ Section 1, 3rd Paragraph – ``Two aquifer pathways exist through aquifer depletion will.'' – confusing sentence – please replace ``through'' with ``by which''.

### 2023-08-01 Writing/NatureWater/1stRoundRevision/replies/reply_to_reviewer_1.tex

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Aquifer thickness versus saturated thickness -- The authors speak of
  \texttt{aquifer\ saturated\ thickness\textquotesingle{}\textquotesingle{},\ which\ is\ a\ redundant\ term.\ Remember,\ the\ definition\ of\ an\ aquifer\ is\ a\ saturated\ unit\ –\ there\ is\ no\ unsaturated\ aquifer.\ Please\ use}aquifer
  thickness'\,' to avoid propagating this confusing usage into the
  future.
\end{enumerate}

\textcolor{blue}{We agree that there is some redundant use of words here. All the instances of ``saturated thickness'' and ``aquifer saturated thickness'' have been replaced by ``aquifer thickness'' in the revised manuscript.}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Dependence on aquifer thickness -- I had a number of questions about
  the relationships displayed in Figure 1. First, the regression appears
  to have been done year by year. Are the quantiles recalculated each
  year to reflect that there may be changes between categories as time
  goes on? Second, when the authors state the lowest quantile goes from
  0 to 33\% are they assuming that the minimum thickness of 9 m is the
  zero point? Third, I assume that the county and year fixed effects are
  calculated as part of the regression. Are there any insights that can
  be gained from the interpretation of those quantities? Fourth, the
  authors need to point out that the same aquifer thickness can result
  in dramatically different transmissive characteristics. Thus, a
  relatively thin aquifer interval composed of coarse sands and gravels
  may be more resilient to drought than a much thicker aquifer dominated
  by fine sands and silts. Could that be a major player in the error
  bars in the plots? Please mention this at some point in the
  manuscript.
\end{enumerate}

\begin{itemize}
\item
  First point:
  \textcolor{blue}{Quantiles are not recalculated each year. If we do so, then the same quantile would represent different aquifer thickness range every year. When modeling the impact of aquifer thickness, this is not desirable because it would be expected that different ranges of aquifer thickness would have the same impact on a farmer's ability to buffer drought risk irrespective of year.}
\item
  Second point:
  \textcolor{blue}{Thank you for highlighting this point. For the 0\% quantile, we assume a saturated thickness of 9m. This minimum of saturated thickness was selected based on \textcolor{red}{Tim, please add REFs}, which defines 9m as the minimum aquifer thickness needed to provide a functioning water supply. We have modified the text on page X lines X-X of the revised manuscript to note these points.}
\item
  Third point:
  \textcolor{blue}{Yes, country and year fixed effects are calculated as part of the regressions. However, these variables can be thought of simply as shifters that tell us how much higher average yields are in a single county relative to another county and to account for trends in yields over time. As these variables do not interact with aquifer thickness in our analysis, there would be little insights gained from analyzing these variables - and indeed it is standard to not report and analyze fixed effects terms in econometric regressions used in statistical crop-climate modeling.}
\item
  Fourth point:
  \textcolor{blue}{This is an important point, which we thank the reviewer for highlighting. The reviewer is correct that unobserved factors, such as aquifer heterogeneity influencing well yield response to changes in saturated thickness, are a likely underlying cause of the uncertainty ranges found in our analyses. Variations in aquifer conductivity would alter the relationship between saturated thickness and well capacity, thereby adding noise to the relationship between saturated thickness and drought risk exposure that would contribute to uncertainty in our estimates of observed relationships between drought impacts and aquifer conditions. \textcolor{red}{(Tim, I am adding this sentence.) This noise is referred to as measurement error in the field of statistics and econometrics, and it has a well-known consequence in regression analysis, called attenuation bias. Specifically, measurement error in an explanatory variable (here, aquifer thickness) tends to bias your estimation in a way that makes the impact of the explanatory variable with measurement errors appear "less" influential than it true is. So, in our context, our estimated impact of aquifer thickness on the share of irrigation is conservative. In reality, the impact of aquifer thickness is likely to be larger.} Importantly though, our analysis shows that - even in the presence of these uncertainties - we are still able to identify statistically significant increases in drought risk exposure for irrigated agriculture as a function of declining saturated thickness. This further reinforces the importance of aquifer conditions as a determinant of adaptive capacity to drought. To highlight these points, we have added the following text in the Discussion section on page 10, the 4th paragraph of our revised manuscript:}
\end{itemize}

\textcolor{blue}{``Similarly, unobserved variations in aquifer properties will also introduce noise into the relationships between aquifer thickness, well yields, and drought risk exposure. For example, a thinner aquifer interval composed of coarse sands and gravels may be able to supply comparable or higher well yields than a thicker aquifer dominated by fine sands and silt deposits, and hence offer greater resilience to drought despite similar or larger aquifer thickness [Butler et al., 2013, Korus and Hensen, 2020]. . These uncertainties can be considered as measurement errors in aquifer thickness as a proxy for well yield. A well-known consequence of measurement errors in regression analysis is attenuation bias [Bound and Krueger, 1991, Hyslop and Imbens, 2001]. That is, measurement error in an explanatory variable (here, aquifer thickness) tends to bias your estimation in a way that makes the impact of the explanatory variable with measurement errors appear "less" influential than it true is. Therefore, it is likely that our estimated impacts of aquifer thickness on drought risk is rather conservative, and the true impact of groundwater depletion is likely to be greater than what we reported in this article. Importantly, however, our analysis shows that - even in the presence of these uncertainties - we are still able to identify statistically significant increases in drought risk exposure for irrigated agriculture as a function of declining saturated thickness. Nonetheless, improved data on spatial variations in aquifer properties and greater monitoring of real-world changes in well capacities alongside traditional water level measurements would help to refine understanding of patterns of drought vulnerability across the HPA. This would enable more precise estimates to be made of critical tipping points in the resilience of irrigated agriculture to drought, which are needed to effectively design and target groundwater conservation policies.''}

@@

\textcolor{blue}{New references added:}

\begin{itemize}
\item
  \textcolor{blue}{Butler, J. J., Stotler, R. L., Whittemore, D. O., and Reboulet, E. C. (2013). Interpretation of water level changes in the High Plains aquifer in western Kansas. Groundwater, 51(2), 180-190.}
\item
  \textcolor{blue}{Korus, J. T., and Hensen, H. J. (2020). Depletion percentage and nonlinear transmissivity as design criteria for groundwater-level observation networks. Environmental Earth Sciences, 79(16), 382.}
\item
  \textcolor{blue}{John Bound and Alan B Krueger. The extent of measurement error in longitudinal earnings data: Do two wrongs make a right? Journal of labor economics, 9(1):1–24, 1991.}
\item
  \textcolor{blue}{Dean R Hyslop and Guido W Imbens. Bias from classical and other forms of measurement error. Journal of Business \& Economic Statistics, 19(4):475–481, 2001}
\end{itemize}

### 2023-08-01 Writing/NatureWater/1stRoundRevision/replies/reply_to_reviewer_2.rmd

---
output:
  pdf_document:
    keep_tex: true
---

\textcolor{blue}{Thank you for the detailed and constructive feedback on our manuscript. We have endeavored to address all your comments and suggestions, and our replies to your comments can found in blue below (original comments in black).}

@@

  - \textcolor{blue}{Korus, J. T., and Hensen, H. J. (2020). Depletion percentage and nonlinear transmissivity as design criteria for groundwater-level observation networks. Environmental Earth Sciences, 79(16), 382.}

  - \textcolor{blue}{Rouhi-Rad, M., Araya, A., and Zambreski, Z. T. (2020). Downside risk of aquifer depletion. Irrigation Science, 38, 577-591.}

2. Though I am not trained as a hydrologist, my understanding is that aquifer saturation thickness is a good measure of general water availability in an aquifer but not necessarily how much water is available at a specific location or point. If this is the case, the authors should make clear why this is an appropriate measure to use in their study and potential limitations of using this approach.

\textcolor{blue}{This is a great point, which is also pointed out by another reviewer. In response, we have added the following texts in the Discussion section on page 10, the 4th paragraph of our revised manuscript.}

\textcolor{blue}{``Similarly, unobserved variations in aquifer properties will also introduce noise into the relationships between aquifer thickness, well yields, and drought risk exposure. For example, a thinner aquifer interval composed of coarse sands and gravels may be able to supply comparable or higher well yields than a thicker aquifer dominated by fine sands and silt deposits, and hence offer greater resilience to drought despite similar or larger aquifer thickness [Butler et al., 2013, Korus and Hensen, 2020]. . These uncertainties can be considered as measurement errors in aquifer thickness as a proxy for well yield. A well-known consequence of measurement errors in regression analysis is attenuation bias [Bound and Krueger, 1991, Hyslop and Imbens, 2001]. That is, measurement error in an explanatory variable (here, aquifer thickness) tends to bias your estimation in a way that makes the impact of the explanatory variable with measurement errors appear "less" influential than it true is. Therefore, it is likely that our estimated impacts of aquifer thickness on drought risk is rather conservative, and the true impact of groundwater depletion is likely to be greater than what we reported in this article. Importantly, however, our analysis shows that - even in the presence of these uncertainties - we are still able to identify statistically significant increases in drought risk exposure for irrigated agriculture as a function of declining saturated thickness. Nonetheless, improved data on spatial variations in aquifer properties and greater monitoring of real-world changes in well capacities alongside traditional water level measurements would help to refine understanding of patterns of drought vulnerability across the HPA. This would enable more precise estimates to be made of critical tipping points in the resilience of irrigated agriculture to drought, which are needed to effectively design and target groundwater conservation policies.''}

@@

3. It is unclear to me why county and time fixed effects were not used in every regression. In particular, it does not look like they were included in the regression that modeled irrigated area as a function of saturated thickness and water deficit. Yet, accounting for time-invariant differences across counties is important, especially because this is the regression that showed the largest effect of saturated thickness on a measure of agricultural production (irrigated area). Is there not enough variation within a county through time to pick up the effect of saturated thickness on irrigated area? This should all be made clearer, and a model that better captures the causal relationship between saturated thickness and area irrigated should be used if possible. If it's not possible, the limitations of the current approach should be made very clear and potential issues with inference.

\textcolor{blue}{Thank you for this comment, which we believe led to a slightly better model and acknowledging important limitations of our methods. County and year fixed effects were included in equation (1), but only year fixed effects were included in equation (2). As you guessed, the problem of including county FEs lies in the massive elimination of variation in aquifer thickness. Please see Figure 6 in Appendix A for the histogram of (1) aquifer thickness demeaned by the county average, (2) aquifer thickness demeaned by the state average, and (3) aquifer thickness without demeaning. As you can see in the figure, inclusion of county FEs (mathematically equivalent to regression using county-demeaned aquifer thickness) dramatically reduces the total variation in aquifer thickness and not enough variations are left for accurately estimating its impact of the share of irrigated acres. The inclusion of State FEs does not diminish the variation in aquifer thickness. Therefore, while the inclusion of State FEs certainly does not provide as tight of a control as county FEs, we have decided to include State FEs for both corn and soybean irrigated share regressions as it is better than not including them. Figure 7 compares the estimated impacts of aquifer thickness with or without State FEs. The negative impact of reduction in aquifer thickness on the share of irrigated acres is slightly greater when state fixed effects are included. Therefore, it may be that aquifer thickness is not very highly correlated with important unobservable variables that are affecting irrigated share significantly. Given the direction of potential bias, providing tighter controls with county fixed effects may result in even more significant drop in the share of irrigated acres (we may be underestimating the impact of aquifer thickness.). All the discussion we are providing here is now seen in Appenddix A.
}

### 2023-08-01 Codes/1_Analysis.rmd
finalized for second submission

```{r}
set.seed(283397)

#--- global parameters ---#
sc_base <- "31011"
sc_dry_base <- "31011_0"

main_analysis <-
  reg_data %>%
  rowwise() %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 50, 90, 130)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_pred_data = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data)
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis(share_reg_data, sat_seq, sandtotal_med, silttotal_med, awc_med)
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))
```

```{r}
#++++++++++++++++++++++++++++++++++++
#+ Bootstrap
#++++++++++++++++++++++++++++++++++++
boot_results_added <-
  main_analysis %>%
  #--- bootsrap data ---#
  dplyr::mutate(boot_data = list(
    replicate(1000, boot(data), simplify = FALSE)
  )) %>%
  #--- get share data ---#
  dplyr::mutate(share_boot_data = list(
    lapply(
      1:length(boot_data),
      \(x) {
        boot_data[[x]] %>%
          .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
          .[, balance_avg := mean(balance), by = sc_code]
      }
    )
  )) %>%
  #--- yield analysis ---#
  dplyr::mutate(yield_pred_data_boot = list(
    parallel::mclapply(
      1:length(boot_data),
      \(x) {
        print(x)
        yield_analysis(boot_data[[x]], balance_seq, sat_seq_eval, sat_breaks, sat_text_data)
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  #--- share analysis ---#
  dplyr::mutate(share_pred_data_boot = list(
    parallel::mclapply(
      1:length(share_boot_data),
      \(x) {
        print(x)
        share_analysis(share_boot_data[[x]], sat_seq, sandtotal_med, silttotal_med, awc_med)
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  #--- average yield analysis ---#
  dplyr::mutate(avg_yield_pred_data_boot = list(
    parallel::mclapply(
      1:length(boot_data),
      \(x) {
        get_average_yield(yield_pred_data_boot[[x]], share_pred_data_boot[[x]])
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::mutate(
    yield_pred_data_boot = list(rbindlist(yield_pred_data_boot)),
    share_pred_data_boot = list(rbindlist(share_pred_data_boot)),
    avg_yield_pred_data_boot = list(rbindlist(avg_yield_pred_data_boot))
  ) %>%
  dplyr::select(
    crop, data, sat_seq, sat_text_data,
    yield_pred_data, yield_pred_data_boot,
    share_pred_data, share_pred_data_boot,
    avg_yield_pred_data, avg_yield_pred_data_boot,
  )

saveRDS(boot_results_added, "Shared/Results/boot_results_added.rds")
```

```{r}
#++++++++++++++++++++++++++++++++++++
#+ Summarize
#++++++++++++++++++++++++++++++++++++
boot_results_added <- readRDS("Shared/Results/boot_results_added.rds")

all_results <-
  boot_results_added %>%
  # rowwise() %>%
  dplyr::mutate(yield_response_sum = list(
    yield_pred_data_boot[, .(
      # y_hat_boot = median(y_hat, na.rm = TRUE),
      y_hat_se = sd(y_hat, na.rm = TRUE),
      # dif_y_hat_boot = mean(dif_y_hat, na.rm = TRUE),
      dif_y_hat_se = sd(dif_y_hat, na.rm = TRUE)
    ),
    by = .(balance, sat, sat_cat)
    ] %>%
      .[yield_pred_data, on = c("balance", "sat")] %>%
      .[, `:=`(
        lower = y_hat - 1.96 * y_hat_se,
        upper = y_hat + 1.96 * y_hat_se,
        dif_lower = dif_y_hat - 1.96 * dif_y_hat_se,
        dif_upper = dif_y_hat + 1.96 * dif_y_hat_se
      )]
  )) %>%
  dplyr::mutate(share_sum = list(
    share_pred_data_boot[, .(
      # ir_share_hat = mean(ir_share_hat, na.rm = TRUE),
      ir_share_hat_se = sd(ir_share_hat, na.rm = TRUE)
    ),
    by = .(sat)
    ] %>%
      .[share_pred_data, on = "sat"] %>%
      .[, `:=`(
        lower = ir_share_hat - 1.96 * ir_share_hat_se,
        upper = ir_share_hat + 1.96 * ir_share_hat_se
      )]
  )) %>%
  dplyr::mutate(avg_yield_sum = list(
    avg_yield_pred_data_boot[, .(
      avg_yield_se = sd(avg_yield, na.rm = TRUE),
      dif_avg_yield_se = sd(dif_avg_yield, na.rm = TRUE)
    ),
    by = .(balance, sat)
    ] %>%
      .[avg_yield_pred_data, on = c("balance", "sat")] %>%
      .[, `:=`(
        upper = avg_yield + 1.96 * avg_yield_se,
        lower = avg_yield - 1.96 * avg_yield_se,
        dif_upper = dif_avg_yield + 1.96 * dif_avg_yield_se,
        dif_lower = dif_avg_yield - 1.96 * dif_avg_yield_se
      )]
  )) %>%
  data.table()

>>>>

```{r}
# ir_share_data <- main_analysis$share_reg_data[[1]]
# sat_seq <- main_analysis$sat_seq[[1]]
# sandtotal_e <- main_analysis$sandtotal_med[[1]]
# silttotal_e <- main_analysis$silttotal_med[[1]]
# awc_e <- main_analysis$awc_med[[1]]

main_analysis <-
  reg_data %>%
  rowwise() %>%
  dplyr::mutate(sc_base = "31011") %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 50, 90, 130)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_analysis_results = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data, sc_base)
  )) %>%
  dplyr::mutate(
    yield_pred_data = list(yield_analysis_results$yield_pred_data),
    yield_semi_res = list(yield_analysis_results$semi_res)
  ) %>%
  dplyr::mutate(yield_dif_test = list(
    lapply(
      2:3,
      \(x) {
        test_dif_in_yield(
          balance_ls = seq(min(data$balance), max(data$balance), length = 50),
          base_q = 1,
          comp_q = x,
          yield_semi_res,
          sat_text_data,
          sc_base
        ) %>%
          .[, comp_q := x]
      }
    ) %>%
      rbindlist()
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis(share_reg_data, sat_seq, sandtotal_med, silttotal_med, awc_med)
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))

saveRDS(main_analysis, "Shared/Results/main_analysis.rds")
```

```{r}
#++++++++++++++++++++++++++++++++++++
#+ Bootstrap
#++++++++++++++++++++++++++++++++++++
set.seed(383954)

all_results <-
  main_analysis %>%
  #--- bootsrap data ---#
  dplyr::mutate(boot_results = list(
    parallel::mclapply(
      1:1000,
      \(x) {
        print(x)

        #--- bootstrap data ---#
        boot_data <- boot(data, sc_base)

        #--- yield analysis ---#
        yield_pred_data <-
          yield_analysis(
            boot_data,
            balance_seq,
            sat_seq_eval,
            sat_breaks,
            sat_text_data,
            sc_base,
            boot = TRUE
          )

        #--- share analysis ---#
        share_boot_data <-
          boot_data %>%
          .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
          .[, balance_avg := mean(balance), by = sc_code]

        share_pred_data <-
          share_analysis(
            ir_share_data = share_boot_data,
            sat_seq,
            sandtotal_med,
            silttotal_med,
            awc_med
          )
        #--- average yield ---#
        avg_yield_pred_data <- get_average_yield(yield_pred_data, share_pred_data)

        return(list(share_pred_data = share_pred_data, avg_yield_pred_data = avg_yield_pred_data))
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::mutate(
    share_pred_data_boot = list(purrr::map(boot_results, "share_pred_data") %>% rbindlist()),
    avg_yield_pred_data_boot = list(purrr::map(boot_results, "avg_yield_pred_data") %>% rbindlist())
  ) %>%
  dplyr::mutate(share_sum = list(
    share_pred_data_boot[, .(
      ir_share_hat_se = sd(ir_share_hat, na.rm = TRUE)
    ),
    by = .(sat)
    ] %>%
      .[share_pred_data, on = "sat"] %>%
      .[, `:=`(
        lower = ir_share_hat - 1.96 * ir_share_hat_se,
        upper = ir_share_hat + 1.96 * ir_share_hat_se
      )]
  )) %>%
  dplyr::mutate(avg_yield_sum = list(
    avg_yield_pred_data_boot[, .(
      avg_yield_se = sd(avg_yield, na.rm = TRUE),
      dif_avg_yield_se = sd(dif_avg_yield, na.rm = TRUE)
    ),
    by = .(balance, sat)
    ] %>%
      .[avg_yield_pred_data, on = c("balance", "sat")] %>%
      .[, `:=`(
        upper = avg_yield + 1.96 * avg_yield_se,
        lower = avg_yield - 1.96 * avg_yield_se,
        dif_upper = dif_avg_yield + 1.96 * dif_avg_yield_se,
        dif_lower = dif_avg_yield - 1.96 * dif_avg_yield_se
      )]
  )) %>%
  data.table() %>%
  dplyr::select(
    crop, data, sat_seq, sat_text_data,
    yield_pred_data,
    yield_dif_test,
    share_pred_data,
    share_sum,
    avg_yield_pred_data,
    avg_yield_pred_data_boot,
    avg_yield_sum
  )
